---
title: "Assignment 1"
author: "Mallika"
date: "8/4/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This analysis uses a Kaggle dataset - https://www.kaggle.com/anandhuh/latest-covid19-india-statewise-data. This dataset contains latest Covid-19 India state-wise data as on August 03, 2021. This dataset can be used to analyze Covid condition in India.

## Load Dataset
```{r echo=TRUE}
CovidCases = read.csv("D:/Business Analysis/Semester 2/INTRO TO ANALYTICS/Assignment/Latest Covid-19 India Status.csv")
CovidCases
```

## Structure of Dataset
```{r echo=TRUE}
str(CovidCases)
```

## List of Variables
```{r echo=TRUE}
names(CovidCases)
```

## Print the top 15 rows of dataset
```{r echo=TRUE}
head(CovidCases , 15)
```

## Function using any of the variables from the data set
```{r echo=TRUE}
TotalActiveCases <- function() { sum(CovidCases$Active)} 
 TotalActiveCases()
```

## Data Manipulation Techniques - Filter rows with Active >20000
```{r echo=TRUE}
library(dplyr)
CovidCasesFiltered <- filter (CovidCases, CovidCases$Active > 20000)
CovidCasesFiltered
```

  


## Create new dataset by joining dependent and independent variables
```{r echo=TRUE}
CovidCasesnew = cbind(CovidCases$State.UTs, CovidCases$Total.Cases, CovidCases$Active)
CovidCasesnew
```
## Convert dataset from "matrix""array" to "data.frame" after cbind()

```{r echo=TRUE}
class(CovidCasesnew)
```

```{r echo=TRUE}
CovidCasesnew = as.data.frame(CovidCasesnew)
class(CovidCasesnew)
```

## Rename column names V1, V2, V3 in CovidCasesnew dataset
```{r echo=TRUE}
names(CovidCasesnew)[1] = "State.UTs"
names(CovidCasesnew)[2] = "Total.Cases"
names(CovidCasesnew)[3] = "Active"
CovidCasesnew
```

## Remove missing values in CovidCases dataset
```{r echo=TRUE}
CovidCases <- na.omit(CovidCases) 
CovidCases
```

## Create duplicated data in dataset
```{r echo=TRUE}
B <- tail(CovidCases, 2)
B
```

## Create new dataset CovidCaseWITHDUP with duplicated data in dataset
```{r echo=TRUE}
CovidCasesWITHDUP = rbind(CovidCases,B) 
CovidCasesWITHDUP
```

## Remove duplicated data in dataset CovidCasesWITHDUP
```{r echo=TRUE}
library(tidyverse)
CovidCasesWITHDUP <- distinct(CovidCasesWITHDUP) 
CovidCasesWITHDUP
```

## Reorder multiple rows in descending alphabetical order of State and Total Cases
```{r echo=TRUE}
CovidCases %>% arrange(desc(CovidCases$State.UTs, Total.Cases)) 
```

## Rename column name State.UTs = X in CovidCases dataset
```{r echo=TRUE}
CovidCases %>% rename(X=State.UTs)
```

## Add new variables/column in dataset by using a mathematical function
```{r echo=TRUE}
CovidCases$Active_Per = (CovidCases$Active.Ratio)*100
CovidCases
```

```{r echo=TRUE}
```


## Add new variables/column in dataset by using a mathematical function
```{r echo=TRUE}
CovidCases$Active_DBL = data.frame(CovidCases$Active.Ratio)*2
CovidCases$Active_DBL
```

## Extract 5 random rows without replacement using random number generator engine
```{r echo=TRUE}
set.seed(1234)
CovidCases %>% sample_n(5, replace = FALSE)
```

## Summary Statistics Dataset
```{r echo=TRUE}
summary(CovidCases)
```

## Mean
```{r echo=TRUE}
mean(CovidCases$Total.Cases)
```
## Median
```{r echo=TRUE}
median(CovidCases$Total.Cases)
```
## Mode
```{r echo=TRUE}
mode(CovidCases$Total.Cases)
```
## Range
```{r echo=TRUE}
range(CovidCases$Total.Cases)
```

## Scatter Plot for Total and Death Ratio
```{r echo=TRUE}
ggplot(CovidCases, aes(x=Total.Cases, y=Deaths))+geom_point()
```
## Bar Plot 
```{r echo=TRUE}
barplot(CovidCases$Deaths, main="Cases",   xlab="States",names.arg = CovidCases$State.UTs)
```


## GIT Repository

https://github.com/mallikashakya/R-prog-assignment-group7




